---
title: "All About Steam Games: Visualizations & Relationships on the 15th of December"
author: "[Afnan Dzaharudin](https://github.com/afnanfdz)"
site: bookdown::bookdown_site
documentclass: book
output:
  bookdown::gitbook:
    css: "style.css"
    split_by: chapter
---

```{r import_dataset, cache = TRUE, echo = FALSE, include = FALSE}
`%>%` <- magrittr::`%>%`

steam = readr::read_csv("https://raw.githubusercontent.com/afnanfdz/datasets/master/steam/steam.csv")
```


# Introduction {-}

Welcome to my first `bookdown` book! Thank you [Yihui Xie](https://yihui.org/en/about/) for this great resource.

## About the book {-}

This book draws from a [single dataset on Steam games on December 15](https://github.com/afnanfdz/datasets/tree/master/steam), that details various information on the 1999 most popular Steam games (by concurrent players that date). Take a look:

```{r show_head_top_ccu, echo = FALSE}
steam %>%
  dplyr::arrange(!ccu) %>%
  DT::datatable(
    options = list(
      scrollX = TRUE,
      pageLength = 5,
      lengthMenu = c(5)
    )
  )
```

#### Why December 15th? {.unlisted -}

That's the date I pulled my dataset from for two projects for two seperate courses that semester. It was also a particularly interesting time for Steam, since December is likely a livelier time for video games, and [Halo Infinite](https://store.steampowered.com/app/1240440/Halo_Infinite/), which was highly anticipated, came out around this time. Furthermore, while the code I used for generating the data _is_ fully automated and reusable (meaning I could easily get a dataset for whenever "today" is when you read this), it does take a long time to run, and, since I've already done work on this dataset before, I can refer to my finished projects to make sure things are consistent (this book is essentially a rewrite, but a lot tidier, better-explained and everything's in one place).

#### Why 1999 games only? {.unlisted -}

If you're asking why I'm 1 less than 2000... off-by-one error.

If you're asking "why not more", it's because past 2000, the games in that category are almost completely unplayed, barely-sold, and such. The game graveyard, or the underside of the iceberg, if you will. These are games that never emerged for one reason or another, and therefore I don't count them in my dataset because I would like to mostly interact with games that _are_ played and _are_ relatively known to the space.

#### Where did the data come from? {.unlisted -}

TODO

## Acknowledgements {-}

This book is a remaster of final projects from two statistics courses:

* STAT 207 (Data Science Exploration), on the Data Science pipeline through Python using `pandas`, `numpy`, `scipy`, `statsmodels`, `matplotlib` and `seaborn`. Taught by [Dr Victoria Ellison](https://vmellison.github.io/index.html).

* STAT 385 (Statistics Programming Methods), on applying our lessons on data wrangling and plotting using `tidyverse` libraries in `R`, to develop a [single Shiny application](https://afnanfdz.shinyapps.io/final_project/). Taught by [Dr David Dalpiaz](https://daviddalpiaz.org/).

My thanks go to both of these instructors for getting me inspired to do data science! Furthermore, Dave's use of `bookdown` for his course websites and textbooks have motivated me further to practice writing my own things in said library, such as this book!
